func-descr.template

### 2025-12-04 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `calc_date_general_effect`.

>>>>

### UMGYE Model: Utility Functions
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) script on _GitHub_.
:::

#### [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) Function {#func.calc_date_general_effect}
\

This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default)of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.

::: { #func.calc_date_general_effect.usage .sidebar }
##### Usage
\
```{r eval=FALSE}
  train_set |>
    calc_date_general_effect(lambda) |>
    calc_UMGY_effect()
```

::: {.noteblock data-latex=""}
In the sample code snippet above the function `calc_date_general_effect` is used internally in the [train_UMGY_effect](#func.train_UMGY_effect)) described below.
:::
:::

::: { #func.calc_date_general_effect.args .sidebar }
##### Arguments
\

::: { #func.calc_date_general_effect.args.train_set .sidebar }
  - **train_set:** Training dataset;

:::
::: { #func.calc_date_general_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

::: { #func.calc_date_general_effect.details .sidebar }
##### Details
\

The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the *Date General Effect* calculated by this function only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.args.lambda) argument, is non-default (to be more exact, greater than zero). The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::

::: { #func.calc_date_general_effect.value .sidebar }
##### Value
\

Data frame representing (*regularized* if [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default) *Date General Effect*.
:::

::: { #func.calc_date_general_effect.code .sidebar }
##### Source Code
\

Below is a simplified version of the source code for the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function:
```{r eval=FALSE}
  dg_effect <- train_set |> 
    left_join(edx.user_effect, by = "userId") |>
    left_join(rglr.UM_effect, by = "movieId") |>
    left_join(rglr.UMG_effect, by = "movieId") |>
    left_join(date_days_map, by = "timestamp") |>
    mutate(resid = rating - (mu + a + b + g)) |>
  group_by(days) |>
    summarise(de = mean_reg(resid, lambda), 
              year = mean(year))

  if(lambda == 0) put_log("Function `calc_date_general_effect`:
Date Global Effect has been computed.")
  else put_log1("Function `calc_date_general_effect`:
Date Global Effect has been computed for lambda: %1...",
                lambda)
  dg_effect
}
```

::: {.noteblock data-latex=""}
The complete source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
:::
:::

#### [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) Function {#func.calc_date_general_effect.cv}
\

Trains (and optionally *regularizes* if the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) the *User+Movie Effect (UME) Model* using the training dataset passed in the [train_set](#func.calc_date_general_effect.cv.args.train_set) argument.

::: { #func.calc_date_general_effect.cv.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
  UM_effect <- calc_date_general_effect.cv(train_set, lambda = 0)
```
:::

::: { #func.calc_date_general_effect.cv.args .sidebar }
##### Arguments
\

::: { #func.calc_date_general_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

::: { #func.calc_date_general_effect.cv.details .sidebar }
##### Details
\

The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero). The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::

::: { #func.calc_date_general_effect.cv.value .sidebar }
##### Value
\

Data frame representing the trained (and also *regularized* if [lambda](#func.calc_date_general_effect.cv.args.lambda) arg value other than default) *UM Effect Model*.
:::

::: { #func.calc_date_general_effect.cv.code .sidebar }
##### Source Code
\

The source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is shown below:
```{r eval=FALSE}
calc_date_general_effect.cv <- function(train_set, lambda = 0){
  if (is.na(lambda)) {
    stop("Function: calc_date_general_effect.cv
`lambda` is `NA`")
  }

::: {.noteblock data-latex=""}
The source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
:::
:::

#### [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) Function {#func.calc_UMGY_effect}
\

::: { #func.calc_UMGY_effect.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
calc_UMGY_effect()

::: { #func.calc_UMGY_effect.args .sidebar }
##### Arguments
\

::: { #func.calc_UMGY_effect.args. .sidebar }
  - **:** ;

::: { #func.calc_UMGY_effect.details .sidebar }
##### Details
\

::: { #func.calc_UMGY_effect.value .sidebar }
##### Value
\

::: { #func.calc_UMGY_effect.code .sidebar }
##### Source Code
\

The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L90) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) script on _GitHub_.
:::
:::

#### [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L42) Function {#func.train_UMGY_effect}
\

Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_effect.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGYE) Model* using the training sample of the `Movielens` dataset (passed in the [train.sgr](#func.train_UMGY_effect.args.train.sgr) argument), specially prepared to train the *UMGYE Model*.

::: { #func.train_UMGY_effect.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
  rglr.UMGY_effect <- edx |> train_UMGY_effect(UMGYE.rglr.best_lambda)
```
:::

::: { #func.train_UMGY_effect.args .sidebar }
##### Arguments
\

::: { #func.train_UMGY_effect.args.train.sgr .sidebar }
  - **train.sgr:** Training sample of the `Movielens` dataset with split rows belonging to multiple genres;

:::
::: { #func.train_UMGY_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

::: { #func.train_UMGY_effect.details .sidebar }
##### Details
\
The dataset passed in the [train.sgr](#func.train_UMGY_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the *Data Helper Functions /* [Data Processing Functions] section of *This Appendix*.

For example, the [`edx.sgr` Object] is an appropriate dataset as the value of the [train.sgr](#func.train_UMGY_effect.args.train.sgr).

::: {.noteblock data-latex=""}
The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, is other than default (to be more exact, greater than zero). The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

::: { #func.train_UMGY_effect.value .sidebar }
##### Value
\

Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_effect.args.lambda) arg value other than default) *UMG Effect Model*.
:::

::: { #func.train_UMGY_effect.code .sidebar }
##### Source Code
\

The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L42) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L42) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L42) script on _GitHub_.
:::
:::

#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) Function {#func.train_UMGY_effect.cv}
\

Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGYE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

::: { #func.train_UMGY_effect.cv.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
  cv.UMGY_effect <- train_UMGY_effect.cv()
```
:::

::: { #func.train_UMGY_effect.cv.args .sidebar }
##### Arguments
\

::: { #func.train_UMGY_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

::: { #func.train_UMGY_effect.cv.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
:::
:::

::: { #func.train_UMGY_effect.cv.value .sidebar }
##### Value
\

Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object]..
:::

::: { #func.train_UMGY_effect.cv.code .sidebar }
##### Source Code
\

The most important part of the source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The complete source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) script on _GitHub_.
:::
:::

#### [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L112) Function {#func.calc_UMGY_effect_MSE}
\

Validates the *UMG Effect (UMGYE) Model* produced by the  [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call.

::: { #func.calc_UMGY_effect_MSE.usage .sidebar }
##### Usage
\

::: { #func.calc_UMGY_effect_MSE.args .sidebar }
##### Arguments
\

::: { #func.calc_UMGY_effect_MSE.args.test_set .sidebar }
  - **test_set:** Validation dataset;

:::
::: { #func.calc_UMGY_effect_MSE.args.umg_effect .sidebar }
  - **umg_effect:** Data frame representing the *UMG Effect Model*.

::: { #func.calc_UMGY_effect_MSE.details .sidebar }
##### Details
\

The function calculates *Mean Squared Error (MSE)* for the *UMGYE Model* passed in the [umg_effect](#func.calc_UMGY_effect_MSE.args.umg_effect) argument using the validation dataset passed in the [test_set](#func.calc_UMGY_effect_MSE.args.test_set) arg.

::: { #func.calc_UMGY_effect_MSE.value .sidebar }
##### Value
\

*MSE* value calculated for the *UMGYE Model*.
:::

::: { #func.calc_UMGY_effect_MSE.code .sidebar }
##### Source Code
\

The source code of the [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L112) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L112) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L112) script on _GitHub_.
:::
:::

#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) Function {#func.calc_UMGY_effect_MSE.cv}
\

Validates the *UMG Effect (UMGYE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

::: { #func.calc_UMGY_effect_MSE.cv.usage .sidebar }
##### Usage
\

::: { #func.calc_UMGY_effect_MSE.cv.args .sidebar }
##### Arguments
\

::: { #func.calc_UMGY_effect_MSE.cv.args.umg_effect .sidebar }
  - **umg_effect:** Data frame representing the *UMG Effect Model*.

::: { #func.calc_UMGY_effect_MSE.cv.details .sidebar }
##### Details
\

The function calculates *MSE* for the *UMGYE Model* passed in the [umg_effect](#func.calc_UMGY_effect_MSE.cv.args.umg_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].

::: { #func.calc_UMGY_effect_MSE.cv.value .sidebar }
##### Value
\

::: { #func.calc_UMGY_effect_MSE.cv.code .sidebar }
##### Source Code
\

The simplified version of the source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The completed source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) script on _GitHub_.
:::
:::

#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) Function {#func.calc_UMGY_effect_RMSE.cv}
\

Validates the *UMG Effect (UMGYE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

::: { #func.calc_UMGY_effect_RMSE.cv.usage .sidebar }
##### Usage
\

::: { #func.calc_UMGY_effect_RMSE.cv.args .sidebar }
##### Arguments
\

::: { #func.calc_UMGY_effect_RMSE.cv.args.umg_effect .sidebar }
  - **umg_effect:** Data frame representing the *UMG Effect Model*.

::: { #func.calc_UMGY_effect_RMSE.cv.details .sidebar }
##### Details
\

The function calculates *Root Squared Error (RMSE)* for the *UMGYE Model* passed in the [umg_effect](#func.calc_UMGY_effect_RMSE.cv.args.umg_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].

::: {.noteblock data-latex=""}
This function internally calls the [calc_user_movie_genre_effect_MSE.cv](#func.calc_user_movie_genre_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGYE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.

::: { #func.calc_UMGY_effect_RMSE.cv.value .sidebar }
##### Value
\

::: { #func.calc_UMGY_effect_RMSE.cv.code .sidebar }
##### Source Code
\

The simplified version of the source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The complete source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) script on _GitHub_.
:::
:::

### 2025-12-04 reports/capstone-movielens.site/work/func-descr.template.Rmd
Function described: `calc_date_general_effect`.

>>>>

### UMGYE Model Regularization
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) script on _GitHub_.
:::

#### [umgye_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) Function {#func.umgye_rglr_helper.tmpl}
\

::: { #func.umgye_rglr_helper.tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
umgye_rglr_helper.tmpl()

::: { #func.umgye_rglr_helper.tmpl.args .sidebar }
##### Arguments
\

::: { #func.umgye_rglr_helper.tmpl.args. .sidebar }
  - **:** ;

:::
::: { #func.umgye_rglr_helper.tmpl.args. .sidebar }
  - **:** ;

::: { #func.umgye_rglr_helper.tmpl.details .sidebar }
##### Details
\

::: { #func.umgye_rglr_helper.tmpl.value .sidebar }
##### Value
\

::: { #func.umgye_rglr_helper.tmpl.code .sidebar }
##### Source Code
\

The source code of the [umgye_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [umgye_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L90) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) script on _GitHub_.
:::
:::
